\large{\bf Looking forwards and backwards: dynamics and genealogies of locally regulated populations }

### 2023-06-05 forwards-and-backwards.tex
.

    As in the proof of Lemma~\ref{lem:eta_compact_containment},
    the Burkholder-Davis-Gundy inequality,
    \citet{barlow/jacka/yor:1986},
    and the fact that $\sqrt{x} \le 1 + x$ for $x \ge 0$
    tells us that there is a $C'$ such that
    \begin{align*}
    \IE\left[ \sup_{0 \le t \le T} M^{h}_t \right]
    & \le
        C'\left( 1 + \IE\left[ [M^{h}]_T \right] \right)
    \\ & \le
        C' \left( 1 + \int_0^T \IE\left[
        \langle 2 c_\theta(x, \eta_s^N) \int_u^\infty h(v)^2 dv
        ,
        \lp_s^N(dx, du) \big \rangle
        \right] ds \right) 
    \\ & \le
        C' \left( 1 + 2 C_a \int_0^\infty h(v)^2 dv
        \int_0^T \IE\left[
            \langle 1 , \lp_s^N(dx, du) \big \rangle
        \right] ds \right)  
    \\ & \le
        C_2 e^{C_1 T} ,
    \end{align*}
    for a constant $C_2$ which is finite
    by our assumption that $\int_0^\infty h(v)^2 dv < \infty$.

@@

Here we record, for completeness, the fact used above
that tightness for a family of processes, if determined by the Aldous-Rebolledo criterion,
extends to sums and products of those processes.
We first record for reference
one version of the Aldous-Rebolledo criteria for tightness of a sequence real-valued processes
(as it appears in \citet{etheridge2000introduction}):

>>>>

    As in the proof of Lemma~\ref{lem:eta_compact_containment},
    the Burkholder-Davis-Gundy inequality,
    \citet{barlow/jacka/yor:1986},
    and the fact that $\sqrt{x} \le 1 + x$ for $x \ge 0$
    tells us that there is a $C'$ such that
    \begin{align*}
    \IE\left[ \sup_{0 \le t \le T} M^{h}_t \right]
    & \le
        C'\left( 1 + \IE\left[ \langle M^{h} \rangle_T \right] \right)
    \\ & \le
        C' \left( 1 + \int_0^T \IE\left[
        \langle 2 c_\theta(x, \eta_s^N) \int_u^\infty h(v)^2 dv
        ,
        \lp_s^N(dx, du) \big \rangle
        \right] ds \right) 
    \\ & \le
        C' \left( 1 + 2 C_a \int_0^\infty h(v)^2 dv
        \int_0^T \IE\left[
            \langle 1 , \lp_s^N(dx, du) \big \rangle
        \right] ds \right)  
    \\ & \le
        C_2 e^{C_1 T} ,
    \end{align*}
    for a constant $C_2$ which is finite
    by our assumption that $\int_0^\infty h(v)^2 dv < \infty$.

@@

Here we record, for completeness, the fact used above
that tightness for a family of processes, if determined by the Aldous-Rebolledo criterion,
extends to sums and products of those processes.
We first record for reference
one version of the Aldous-Rebolledo criteria for tightness of a sequence real-valued processes
(as it appears in Theorem~1.17 of \citet{etheridge2000introduction};
see also Theorem~4.13 of \citet{jacod/shiryaev:2013}):
